\section{Experiments}
This section reports the results that are actually supported by the current repository release. We evaluate synthetic-only training and synthetic-plus-weaklabel training. Real-pilot and raw-video experiments remain out of scope for this version.

\subsection{Metrics}
Timing prediction is evaluated with accuracy, balanced accuracy, macro-F1, and per-class precision/recall/F1. Because the timing labels are imbalanced, balanced accuracy and macro-F1 are the primary metrics. Strategy prediction is evaluated with strategy accuracy and strategy macro-F1. For the multitask model, we additionally report state MAE. For the tri-modal emotion encoder, we report fine-emotion accuracy, balanced accuracy, macro-F1, valence MAE, arousal MAE, and auxiliary state MAE.

\subsection{Protocol}
The formal experiments reported here were trained on two NVIDIA A800 80GB GPUs using the \texttt{remote\_a800.yaml} setting. Synthetic training uses a 24{,}000/2{,}400/2{,}400 split; mixed training augments the synthetic train split with 286 weak-label training episodes extracted from historical logs and evaluates on both the held-out synthetic split and the held-out weaklabel split. The bridge-log parser is implemented but not included in the main experiments because its current volume is too small for stable training conclusions.

Two caveats are essential for interpreting the tables. First, the synthetic benchmark is now a real three-class task, but it is still rule-generated and therefore measures rule-recovery plus temporal generalization rather than natural in-the-wild behavior. Second, the combined test columns in Table~\ref{tab:main-results} merge the 2{,}400-window synthetic test set with the 62-window weaklabel test set, so they are dominated by synthetic windows and should be treated as aggregate diagnostics rather than as a proxy for real-world robustness.

\subsection{Main Results}
\input{tables/main_results}

Three findings are robust across the current runs. First, on the held-out synthetic split the temporal models are now credible three-class timing baselines, and the joint branch is strongest overall at 86.90\% balanced accuracy and 81.06\% timing Macro-F1, with the structured sanity baseline close behind at 85.56\% and 79.11\%. Second, mixed training improves the aggregate offline numbers for the joint branch, but the combined columns remain synthetic-heavy; the strongest held-out weaklabel timing Macro-F1 is still only 36.29\%. Third, the multitask branch remains important because it is the only current model that predicts latent state directly, reaching a state MAE of 0.069 on synthetic-only training and 0.083 under mixed training.

\subsection{Weaklabel Generalization}
\input{tables/weaklabel_results}

Held-out weaklabel performance remains the hardest setting. The exploratory joint model is strongest on weaklabel timing Macro-F1 at 36.29\%, the structured baseline reaches 27.29\%, and the multitask model drops to 7.62\%. Strategy transfer is weaker still: the best held-out weaklabel strategy Macro-F1 is only 22.50\% from the structured baseline, while the joint model reaches 18.06\%. These numbers are useful as a bootstrapping signal, not as proof of real-world robustness. They mainly quantify the current synthetic-to-log mismatch and motivate future raw-video ingestion, stronger weaklabel reconstruction, and real-pilot collection.

\subsection{Tri-Modal Emotion Benchmark}
\input{tables/trimodal_results}

The new tri-modal benchmark tests the perception layer in isolation. Full fusion reaches 97.59\% accuracy and 97.58\% Macro-F1 on the held-out synthetic benchmark, while also keeping valence MAE at 0.068 and arousal MAE at 0.055. The ablations are more informative than the headline number: face-only, motion-only, and audio-only settings collapse to 24.33\%, 8.33\%, and 31.11\% accuracy, respectively. On this controlled benchmark, fusion is not a marginal gain but the core source of performance.

\subsection{Tri-Modal Care Relation Benchmark}
\input{tables/trimodal_care_results}

The second tri-modal benchmark asks a harder question: can the same multimodal encoder predict whether the user needs care and whether the appropriate action is \texttt{none}, \texttt{delay}, or \texttt{immediate}? Full fusion reaches 99.45\% care-need AUROC, 97.85\% care-need F1, and 94.00\% care-timing Macro-F1. The ablations reveal a more nuanced picture than in the emotion benchmark. Face-only remains surprisingly strong for binary care-need prediction, but its timing Macro-F1 drops to 51.88\%, while motion-only and audio-only collapse almost entirely. On this synthetic benchmark, binary concern detection is easier than timing-specific intervention planning, and full fusion matters more for the latter.

\subsection{Status Audit}
\input{tables/audit_table}
